Comparative Evaluation of Spark and Flink Stream Processing

### 2017-02-25 paper/paper.tex
small refinements

\begin{flushleft}
\centering\LARGE {\bf Comparative Evaluation of Spark and Flink Stream Processing}
\thispagestyle{empty}
\end{flushleft}
\newpage
\tableofcontents

@@

\par The rest of this paper is organized as follows: Section 2
presents the main characteristics, APIs, and main data abstraction of Spark and Flink. Section 3  describes the experiment workloads and their implementation in each framework. Section 4
provides and compares the performance results of the different workloads. Finally, Section 5 gives the overall conclusion.

@@

\subsection{Evaluation Streaming Workloads}
In our experimental evaluation, we developed two real-time stream processing workloads that read the ADS-B messages stream from Kafka in order to perform basic trajectories analysis methods. In our design choice, we try to cover some key points that related to the streaming processing tasks, and evaluate the corresponding solutions in Spark and Flink. The following are general key aspects of  streaming data processing were covered by our workloads's design:

@@

@@

     \caption{Flink implementation of statistics computation workload.}
\end{figure}

>>>>

\begin{flushleft}
\centering\LARGE {\bf Comparative Evaluation of Spark and Flink Stream Processing}

Supervisor: PD Dr. Michael Mock
\thispagestyle{empty}
\end{flushleft}
\newpage
\tableofcontents

@@

\par The remainder of this paper is organized as follows.
In Section 2, we present the main characteristics, APIs, and main data abstraction of Spark and Flink. Section 3  describes the experiment workloads and their implementation in each framework. Section 4
provides and compares the performance results of the different workloads. Finally, Section 5 gives the overall conclusion.

@@

\subsection{Evaluation Streaming Workloads}
In our experimental evaluation, we developed two real-time stream processing workloads that read the ADS-B messages stream from Kafka in order to perform basic trajectories analysis methods. The workloads are designed in such way that cover general key aspects of real-time streaming processing tasks, and evaluate the corresponding solutions in Spark and Flink. The following are the aspects of streaming data processing were covered by our workloads's design:

@@

The detail of Flink's implementation of statistics computation workload as follows. First, \texttt{map}

@@
